Andres Karjus

### 2018-04-15 index.Rmd
evolang talk slides

- [The inaugural meeting of the Society for Computation in Linguistics](https://blogs.umass.edu/scil/scil-2018/), part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | [poster pdf](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl)
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/)
- [51st Annual Meeting of the Societas Linguistica Europaea](http://sle2018.eu/)

>>>>

- [The inaugural meeting of the Society for Computation in Linguistics](https://blogs.umass.edu/scil/scil-2018/), part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | download [poster](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl) | download [slides](https://drive.google.com/open?id=10az7BOV_tT-mAwMZXDoguKmZeTErnfzB)
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/)
- [51st Annual Meeting of the Societas Linguistica Europaea](http://sle2018.eu/)
